---
title: "Studies class 1 Spring 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Study 1

Each person will guess a number between 0 and 100. The person closest to 65% of the average of everyone else wins.

```{r guesses}
names = c("Albina","Kilsy","Wen Jian","Garima","Judith","Andres","Pablo","Aelen","Jose","Chad","Grabiel")
guesses = c(65,50.5,70,33,55,37,40.05,28.5,33.333,30,70)
xbar1 = mean(guesses)
n1 = length(guesses)
s1 = sd(guesses)
hist(guesses,breaks=10)
xbar1
0.65*xbar1
s1
```
We now make a confidence interval based on our sample. We are inferring about the true population average. $$\mu \approx \bar{x}\pm t^{\star} SE $$
We need $t^\star$. We assume $CL = 95\%$.

```{r tstar}
tstar1 = round(qt(0.975,n1-1),2)
tstar1
```
We need standard error. $$SE_1 = \frac{s_1}{\sqrt{n}} $$
```{r standard error}
SE1 = s1/sqrt(n1)
SE1
```
```{r CI}
LB1 = xbar1-tstar1*SE1
UB1 = xbar1+tstar1*SE1
print(c(LB1,UB1)) 
print(c(LB1,UB1)*0.65) #best future guess...
```

Now, we repeat the game.
```{r repeat game}
guesses2 = c(53, 29, 28.3, 36, 47, 41, 34, 29.8, 100, 20, 25)
xbar2 = mean(guesses2)
s2 = sd(guesses2)
n2 = length(guesses2)
xbar2
0.65*xbar2
s2
```


```{r differences}
 diffs = guesses2-guesses
diffs
xdiff = mean(diffs)
xdiff
sdiff = sd(diffs)
sdiff
```

We are going to test for whether the difference is significant.
$$H_0:~~ \mu_\text{diff} = 0 $$
$$H_A:~~ \mu_\text{diff} \ne 0 $$
We will use $\alpha = 0.05$. We find $t^\star = 2.23$.
$$SE_\text{diff} = \frac{s_\text{diff}}{\sqrt{n}} $$
```{r SEdiff}
SEdiff = sdiff/sqrt(n1)
SEdiff
```
We find $t_\text{obs}$.

$$t_\text{obs} = \frac{\overline{x_\text{diff}}-(\mu_\text{diff})_0}{SE_\text{diff}} $$

```{r tobs}
tobs = (xdiff/SEdiff)
tobs
```



