\documentclass[12pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
\urlstyle{same}

\usepackage{tabularx}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{multirow,array}
\usepackage{newtxtext,newtxmath}
\usepackage{relsize}
\usepackage{lastpage}
\usepackage{enumitem}
\usepackage{adjustbox}
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\pagestyle{fancy}
\fancyhf{}
\lhead{\textsc{BHCC Mat-181}}
\chead{\textsc{Answers}}
\rhead{\textsc{Exercises 1.17-1.29}}
\rfoot{Page \thepage ~of \pageref*{LastPage}}
\setenumerate[1]{label={\bf 1.\theenumi: }}
\setenumerate[2]{label={\bf (\theenumii): }}

\begin{document}

\begin{enumerate}
\setcounter{enumi}{16}
\item \begin{enumerate}
\item Observational study
\item It is natural to use a stratified sampling method, about 10 students from each group.
\end{enumerate}

\item \begin{enumerate}
\item Observational study
\item It is natural to use stratified sampling. The strata would be the 4 years. You would then randomly sample from each strata.
\end{enumerate}

\item \begin{enumerate}
\item There is a positive, nonlinear association between life expectancy and internet participation.
\item Observational study.
\item Countries that are more set up to use fossil fuels have higher life expectancies and higher internet participation.
\end{enumerate}

\item \begin{enumerate}
\item Observational study.
\item No. This study can not show a causal relationship.
\item More caffeine or less sleep.
\end{enumerate}

\item \begin{enumerate}
\item Reasonable!
\item Sure... I wonder why we think different fields would have different opinions on the student union. But, if we wanted to be sure to get every field represented, it is fine.
\item Ages would not be clusters. I imagine the younger students are probably more interested in improving the student union, because they are more likely to be around to enjoy the improvements.
\end{enumerate}

\item Gallup Poll is fighting a bias stemming from who is more likely to have a number in a phonebook -- older people with land lines.

\item \begin{enumerate}
\item The 200 participants.
\item Disposition toward camping, disposition toward health care, disposition toward architecture, etc...
\item Disposition toward microwave oven.
\item Yes, the study uses random sampling.
\item Observational study. There is no assignment to experimental groups.
\item No. We can not establish a causal link.
\item Yes. The sampling was random.
\end{enumerate}

\item Well, we are more likely to ask a child from a large family because a large family probably has more children at the school. This will cause an overestimation of the true value. Of course, this could be corrected for...

\item \begin{enumerate}
\item Response bias. A parent who has time is more likely to fill out the survey.
\item Hmm... there might be a link between whether a woman moved and whether the child has respiratory problems. I'm not exactly sure what story makes most sense here. Maybe if a child has respiratory problems, the mother will be more likely to consider moving out of the city?
\item Maybe they run because they don't have joint pain.
\end{enumerate}

\item \begin{enumerate}
\item Random sampling is always good.
\item This stratified sampling could be fine.
\item I'd worry about missing voices from a distinct neighborhood. I don't think this is effective.
\item I'd worry about the same issue as with the previous method.
\item This convenience sample is laughably bad.
\end{enumerate}

\item \begin{enumerate}
\item Random sampling with the possibility of non-response bias.
\item Convenience sample, probably biased somehow.
\item Convenience sample, similar to problem above.
\item Multistage sampling. This might be fine, but I imagine there might be different relationships in different classes (like, math classes might show a stronger negative association than philosophy classes), so the sample might not be representative.
\end{enumerate}

\item \begin{enumerate}
\item We should not conclude a causal relationship. It is an observational study. Maybe those with dementia are more likely to smoke.
\item Nope. Maybe the causal relationship goes the other way. Maybe bullies feel bad, and that effects their sleep. Also, maybe a third confounding variable causes both (like trouble at home).
\end{enumerate}

\item I'd guess most Facebook users are not college students who have joined a psychology participation pool and are interested in this study. This sounds quite biased, so we can not generalize to the population.

\end{enumerate}
\end{document}