\documentclass[12pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{multicol}
\usepackage{lastpage}
\usepackage{fancyhdr}
\usepackage{multirow,array}
\usepackage{newtxtext,newtxmath}
\usepackage{lastpage}
\usepackage{enumitem}
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\pagestyle{fancy}
\fancyhf{}
\lhead{\textsc{BHCC Mat-181}}
\chead{\textsc{Answers}}
\rhead{\textsc{HW Exercises 1.65-1.68}}
\rfoot{Page \thepage ~of \pageref{LastPage}}
\setenumerate[1]{label={\bf 1.\theenumi: }}
\setenumerate[2]{label={\bf (\theenumii): }}


\begin{document}
\begin{enumerate}
\setcounter{enumi}{64}

\item \begin{enumerate}
\item The bar chart allows the reader to get an accurate numerical values of the relative frequencies. The bar plot also makes it clearer that cardiovascular has higher proportion than respiratory. 
\item Maybe the pie chart makes more obvious that the proportions add up to 1, but you should know relative frequencies add to 1.
\item The bar chart!
\end{enumerate}


\item \begin{enumerate}
\item $\frac{372}{910} \approx 40.9\%$
\item $\frac{278}{910} \approx 30.5\%$
\item $\frac{57}{910} \approx 6.3\%$
\item We are now calculating part-of-part proportions.
\begin{center}
\begin{tabular}{|c | c | c |} \hline
ideology & fraction in favor of citizenship option & percentage in favor of citizenship option \\ \hline
conservative & $\frac{57}{372}$ & 15.3\% \\ &&\\
moderate & $\frac{120}{363}$ & 33.1\% \\ && \\
liberal & $\frac{101}{175}$ & 57.7\% \\ \hline
\end{tabular}
\end{center}
\item Ideology and view are not independent. The liberals have a higher proportion in favor than moderates, who have a higher proportion in favor than conservatives. If ideology and view were independent, these part-of-part proportions would be similar.
\end{enumerate}

\item Views on DREAM Act and political ideology are not independent. If they were independent, the mosaic plot's horizontal breaks (determining the heights of rectangles) would be continuous across the whole plot.

\item Party and views on taxes are not independent.  If they were independent, the mosaic plot's horizontal breaks (determining the heights of rectangles) would be continuous across the whole plot.

\end{enumerate}
\end{document}
