\begin{frame}
\frametitle{Textbook}
\begin{itemize}
\item Our textbook is called OpenIntro Statistics. 
\item \webURL{www.openintro.org}
\item A digital version is free to download.
\item Videos!
\item Print copies are available for \$15.
\item \webURL{www.amazon.com/dp/1943450048}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Chapters}
\begin{description}
\setlength{\itemsep}{0mm}
\item[1. Introduction to data.] Data structures, variables, summaries, graphics, and basic data collection techniques.
\item[2. Probability.] The basic principles of probability.
\item[3. Distributions of random variables.] Introduction to the normal model and other key distributions.
\item[4. Foundations for inference.] General ideas for statistical inference in the context of estimating the population mean.
\item[5. Inference for numerical data.] \hspace{1mm}Inference for one or two sample means using the \mbox{$t$-distribution}, and also comparisons of many means using ANOVA.
\item[7. Introduction to linear regression.] An introduction to regression with two variables. Most of this chapter could be covered after Chapter~1.
\end{description}
\end{frame}

\begin{frame}
\frametitle{Examples and Guided Practice}
\begin{itemize}
\item[\color{oiB}\Large$\CIRCLE$]\noindent\textbf{\color{oiB}Example 0.1}\hspace{0.3cm}
Large filled bullets signal the start of an example. Full solutions to examples are provided and may include an accompanying table or figure.
\item[\color{oiB}$\bigodot$]\noindent\textbf{\color{oiB}Guided Practice 0.2}\hspace{0.3cm}
Large empty bullets signal an exercise for additional practice and guidance. Students may find it useful to fill in the bullet after understanding or successfully completing the guided practice. Solutions are provided in the footnotes.
\end{itemize}
\end{frame}

